### 2024-12-03 README.Rmd
fix typos

embedplyr enables common operations with word and text embeddings within a 'tidyverse'/'quanteda' workflow, as demonstrated in [Data Science for Psychology: Natural Language](http://ds4psych.com).

@@

``` r
# devtools package required to install quanteda from Github 
remotes::install_github("rimonim/embedplyr") 
```

>>>>

embedplyr enables common operations with word and text embeddings within a 'tidyverse' and/or 'quanteda' workflow, as demonstrated in [Data Science for Psychology: Natural Language](http://ds4psych.com).

@@

``` r
remotes::install_github("rimonim/embedplyr") 
```
